Postural developments mediate children's visual access to social information

### 2018-01-25 writeup-cogsci/cogsci2018_faceOnly.Rmd

### READ IN GROUND TRUTH
ground_truth_faces <- read_csv("../data/ground_truth/ground_truth_faces.csv") %>%
  mutate(sample_type=as.factor(sample_type))

@@

# run models
glm_faces<-glm(y_faces ~ dGLM_faces$age.at.test * dGLM_faces$posture * dGLM_faces$orientation,family=binomial(logit))
xtable(summary(glm_faces))

@@

## OUTPUT GLM RESULTS
cleanedNames = c("Intercept","Age","Prone","Sit","Stand","Close","Far", "Age:Prone","Age:Sit","Age:Stand","Age:Close",
          "Age:Far","Prone:Close","Sit:Close","Stand:Close","Prone:Far","Sit:Far","Stand:Far","Age:Prone:Close",
          "Age:Sit:Close","Age:Prone:Far","Age:Sit:Far")
faceGLMOut=xtable(summary(glm_faces))
rownames(faceGLMOut)<-cleanedNames

@@

@@

```{r results="asis"}
print(faceGLMOut, type="latex", comment = F, table.placement = "H")
print(wristGLMOut, type="latex", comment = F, table.placement = "H")
```

<!-- # # output results -->
<!-- normalGLM <- normalGLM %>% -->
<!--   xtable %>% -->
<!--   print(type="latex", comment = F, table.placement = "H") -->

<!-- # ## Then try a run mixed effet model -->
<!-- # ## Interactions fail to converge, as does the one below -->
<!-- # fullModelminsInt_Faces_MTCNN <- glmer(faceMT ~ scale(age.at.test)+(posture)+(orientation) + (1|subid), -->
<!-- #        data = d, -->
<!-- #        family = "binomial") -->

<!-- ## Reading https://rdrr.io/cran/lme4/man/convergence.html -->
<!-- ## Check for singularity - not an issue -->
<!-- # fm1=fullModelminsInt_Faces_MTCNN -->
<!-- # diag.vals <- getME(fm1,"theta")[getME(fm1,"lower") == 0] -->
<!-- # any(diag.vals < 1e-6) # FALSE -->

<!-- ## But has issues with every optimizer... -->
<!-- #source(system.file("utils", "allFit.R", package="lme4")) -->
<!-- #fm1.all <- allFit(fm1) -->
<!-- #ss <- summary(fm1.all) -->

<!-- #No convergence issues with open pose detectors -->
<!-- fullModelminsInt_Faces_OP <- glmer(faceOP ~ scale(age.at.test) + posture + orientation + (1|subid), -->
<!--        data = d, -->
<!--        family = "binomial") -->

<!-- fullModelminsInt_Wrist_OP <- glmer(wristOP ~ scale(age.at.test) + posture + orientation + (1|subid), -->
<!--        data = d, -->
<!--        family = "binomial") -->
<!-- ``` -->

@@

<!-- ```{r MTCNNModel, results="asis"} -->
<!-- tab2 <- xtable::xtable(summary(fullModelminsInt_Faces_MTCNN)$coef, digits=3, -->
<!--                       caption = "Results from GLMM model predicting the presence/absence of a face (MTCNN-Faces) across the entire dataset.") -->

<!-- print(tab2, type="latex", comment = F, table.placement = "H") -->
<!-- ``` -->

<!-- ```{r OPModel, results="asis"} -->
<!--  tab3 <- xtable::xtable(summary(fullModelminsInt_Faces_OP)$coef, digits=3, -->
<!--                        caption = "Results from GLMM model prediting the presence/absence of faces (OpenPose-Faces) across the entire dataset.") -->

<!--  print(tab3, type="latex", comment = F, table.placement = "H") -->
<!-- ``` -->

@@

# ```{r session_info, include=FALSE, echo=FALSE}
# devtools::session_info()
# ```

>>>>

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}
### READ IN GROUND TRUTH
ground_truth_faces <- read_csv("../data/ground_truth/ground_truth_faces.csv") %>%
  mutate(sample_type=as.factor(sample_type))

@@

# run models
glm_faces<-glm(y_faces ~ dGLM_faces$age.at.test * dGLM_faces$posture * dGLM_faces$orientation,family=binomial(logit))

glm_faces_noInt<-glm(y_faces ~ dGLM_faces$age.at.test + dGLM_faces$posture + dGLM_faces$orientation,family=binomial(logit))

@@

glm_wrists_noInt<-glm(y_wrists ~ dGLM_wrists$age.at.test + dGLM_wrists$posture + dGLM_wrists$orientation,family=binomial(logit))

## OUTPUT GLM RESULTS
cleanedNames_NoInt = c("Intercept","Age","Prone","Sit","Stand","Close","Far")
cleanedNames = c("Intercept","Age","Prone","Sit","Stand","Close","Far", "Age:Prone","Age:Sit","Age:Stand","Age:Close",
          "Age:Far","Prone:Close","Sit:Close","Stand:Close","Prone:Far","Sit:Far","Stand:Far","Age:Prone:Close",
          "Age:Sit:Close","Age:Prone:Far","Age:Sit:Far")

faceGLMOut=xtable(summary(glm_faces))
rownames(faceGLMOut)<-cleanedNames

@@

wristGLMOut_noInt=xtable(summary(glm_wrists_noInt))
rownames(wristGLMOut_noInt)<-cleanedNames_NoInt

faceGLMOut_noInt=xtable(summary(glm_faces_noInt))
rownames(faceGLMOut_noInt)<-cleanedNames_NoInt

@@

```{r results="asis"}
print(faceGLMOut_noInt, type="latex", comment = F, table.placement = "H")
```

```{r results="asis"}
print(wristGLMOut_noInt, type="latex", comment = F, table.placement = "H")
```

```{r echo=FALSE, include=FALSE}
## Mixed effect model tries - many convergence issues

 # Interactions fail to converge, as does the one below 
 # fullModelminsInt_Faces_MTCNN <- glmer(faceMT ~ scale(age.at.test)+(posture)+(orientation) + (1|subid), 
 #        data = d, 
 #        family = "binomial")

## Reading https://rdrr.io/cran/lme4/man/convergence.html 
## Check for singularity - not an issue 
# fm1=fullModelminsInt_Faces_MTCNN 
# diag.vals <- getME(fm1,"theta")[getME(fm1,"lower") == 0] 
# any(diag.vals < 1e-6) # FALSE

## But has issues with every optimizer... -->
#source(system.file("utils", "allFit.R", package="lme4")) 
#fm1.all <- allFit(fm1)
#ss <- summary(fm1.all)

#No convergence issues with open pose detectors for faces, but for wrists
#fullModelminsInt_Faces_OP <- glmer(faceOP ~ scale(age.at.test) + posture + orientation + (1|subid), 
#      data = d, 
#        family = "binomial") 
```

@@

@@

 ```{r session_info, include=FALSE, echo=FALSE}
 devtools::session_info()
 ```
